---
title: "Building an Anthropic API Wrapper"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example-Anthropic-API-wrapper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wrapify)
```

## The `wrapper` object

Referring to the [getting started](https://docs.anthropic.com/en/api/getting-started) section of the Anthropic documentation, there's a useful example call.

```bash
curl https://api.anthropic.com/v1/messages \
     --header "x-api-key: $ANTHROPIC_API_KEY" \
     --header "anthropic-version: 2023-06-01" \
     --header "content-type: application/json" \
     --data \
'{
    "model": "claude-3-5-sonnet-20241022",
    "max_tokens": 1024,
    "messages": [
        {"role": "user", "content": "Hello, world"}
    ]
}'
```

This shows that the requests should be sent to `https://api.anthropic.com/v1/{endpoint}`, with headers `"anthropic-version: 2023-06-01"`, `"content-type: application/json"`, and the API key using the header `x-api-key`. This is all the information we need to create the wrapper object.

```{r wrapper}
anth_wrapper <- wrapper(
  base_url = "https://api.anthropic.com/v1",
  auth = header_auth_type("x-api-key"),
  default_headers = list(
    "content-type" = "application/json",
    "anthropic-version" = "2023-06-01"
  ),
  env_var_name = "ANTHROPIC_API_KEY"
)
```

The wrapper object is really just a special list which holds on to basic data that will be used by any requestor function. All that needs to be specified is the `base_url`, but specifying other things will make things easier downstream. Specifying an `env_var_name` allows requestor functions to obtain credentials from an environment variable.

## The `requestor` function

Now we will build a requestor which hits the [/messages](https://docs.anthropic.com/en/api/messages) endpoint. Referring to [the documentation](https://docs.anthropic.com/en/api/messages), we need to send a `POST` with a body containing, at least, the parameters:

- model
  - which model to use
- messages
  - a list of message objects of the form {"role": "user", "content": "Hello, Claude"}
- max_tokens
  - The maximum number of tokens to generate before stopping

It's straightforward to just read this off as a call to `requestor`.

```{r}
messages <- requestor(
  anth_wrapper,
  resource = "messages",
  method = "post",
  body_args = function_args(
    messages = , # blank RHS for no default
    model = "claude-3-5-sonnet-latest", # assign a default value
    max_tokens = 200
  )
)
```

This creates a function `messages` which hits the API. The handy `generate_roxygen_comment` function can output a Roxygen skeleton for this function.

```{r}
generate_roxygen_comment(
  messages, 
  title = "Messages endpoint", 
  description = "Hit the messages endpoint", 
  param_descriptions = list("messages" = "A list of messages",
                            "model" = "Which model to use",
                            "max_tokens" = "Max number of tokens to return"))
```
This will use the API key given in `.credentials` if supplied, or otherwise, will look for the default credential supplied by the wrapper. Here's how a call looks.

```{r}
msg <- list(list(role = "user", content = "What is the square root of 81?"))  # messages need to be supplied in this format
response <- messages(msg)
response
```

By default, the `messages` function performs the request and extracts the response. It can sometimes be the case that we don't want this behavior—for example, if we want to generate a bunch of requests locally first and then send them all at once using `httr2::req_perform_*` or something like that. To avoid performing the request, just set the `.perform` argument to `FALSE`. This will return the raw `request` object.

```{r}
messages(msg, .perform = FALSE)
```

You may also wish to perform the request but not extract the data. This can be done by setting `.extract` to `FALSE`.

```{r}
messages(msg, .extract = FALSE)
```

Either of these can be set as the default behavior for a requestor function by specifying it.

```{r}
messages_not_default_send <- requestor(
  anth_wrapper,
  resource = "messages",
  method = "post",
  body_args = function_args(
    messages = , # blank RHS for no default
    model = "claude-3-5-sonnet-latest", # assign a default value
    max_tokens = 200
  ), 
  perform_by_default = FALSE
)

# not sent
messages_not_default_send(msg)
```

### Custom extractor

It's often the case that we're not ultimately interested in the full data that is returned, but some derivative of it. If you write a function that extracts and shapes the data that you're looking for, you can supply it to the requestor. The extractor function should take the `httr2::response` object.

```{r}
extract_message_text <- function(x) {
  data <- httr2::resp_body_json(x)
  data$content[[1]]$text
}
messages(msg, .extractor = extract_message_text)
```

If you want, you can specify this as the default extractor when the requestor function is defined.

```{r}
messages <- requestor(
  anth_wrapper,
  resource = "messages",
  method = "post",
  body_args = function_args(
    messages = , # blank RHS for no default
    model = "claude-3-5-sonnet-latest", # assign a default value
    max_tokens = 200
  ),
  extractor = extract_message_text
)
messages(msg)
```

Of course, even with a custom extractor set, you can always elect not to extract the content if you want.

```{r}
messages(msg, .extract = FALSE)
```

## Constructors

Notice that the API requires us to provide a list of messages in a particular format. There's a simple helper called `super_simple_constructor` that lets us do that a bit more quickly.

```{r}
message <- super_simple_constructor(content =, role = "user")
message("Hello")
```
This just creates a simple constructor of a named list in the format that we need. This way, we can call the requestor as follows.

```{r}
messages(list(message("Hi there. What is 2 * 19?")))
```

## Putting it all together

Putting it all together, here's the full code for a fairly full-featured Claude wrapper.

```{r}
anth_wrapper <- wrapper(
  base_url = "https://api.anthropic.com/v1",
  auth = header_auth_type("x-api-key"),
  default_headers = list(
    "content-type" = "application/json",
    "anthropic-version" = "2023-06-01"
  ),
  env_var_name = "ANTHROPIC_API_KEY"
)

message <- super_simple_constructor(content = , role = "user")

messages <- requestor(
  anth_wrapper,
  resource = "messages",
  method = "post",
  body_args = function_args(
    messages = , # blank RHS for no default
    model = "claude-3-5-sonnet-latest", # assign a default value
    max_tokens = 200
  ),
  extractor = extract_message_text
)
```
